% Chapter 3

\chapter{Properties of Hankel Operators} % Main chapter title

\label{PropertiesOfHankelOperators} % For referencing the chapter elsewhere, use \ref{Chapter1} 

\lhead{Chapter \ref{PropertiesOfHankelOperators}. \emph{Properties of Hankel Operators}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------


\section{Definition of a Hankel matrix}
A Hankel matrix is an infinite matrix $\{M_{j,k}\}_{j,k \geq 0}$
whose $(j,k)th$ entry depends only on $j+k$. If $a = \{a_j\}_{j\geq 0}$,
Let $M_a = \{a_{j+k}\}_{j,k\geq 0}$ be the Hankel matrix with $(j,k)$th
entry $a_{j+k}$. That is,
\begin{equation}
    M_a = \begin{pmatrix}
        a_0 & a_1 & a_2 & a_3 & \cdots\\
        a_1 & a_2 & a_3 & a_4 & \cdots\\
        a_2 & a_3 & a_4 & a_5 & \cdots\\
        a_3 & a_4 & a_5 & a_6 & \cdots\\
        \vdots & \vdots & \vdots & \vdots & \ddots
    \end{pmatrix}.
\end{equation}
An infinite matrix does not necessarily define an operator on $\ell^2(\Ntrl)$, 
however any infinite matrix can be identified with a linear operator 
on the dense subset $c_{00}(\Ntrl) \subset \ell^2(\Ntrl)$ of sequences
of finite support. 

For a sequence $a \in c_{00}(\Ntrl)$, and an infinite matrix $M = (M_{j,k})_{j,k\geq 0}$, 
we define $Ma \in c_{00}(\Ntrl)$ as $Ma = \{\sum_{k=0}^\infty M_{j,k}a_k\}_{j=0}^\infty$.

Hence we shall interchangeably talk about infinite matrices and linear
operators $c_{00}(\Ntrl)\rightarrow c_{00}(\Ntrl)$.

Since $c_{00}(\Ntrl)$ is dense in $\ell^2(\Ntrl)$, if an infinite matrix
considered as an operator on $c_{00}(\Ntrl)$ is bounded on $c_{00}(\Ntrl)$
in the $\ell^2$-norm, then the matrix extends uniquely to an operator on $\ell^2(\Ntrl)$.
Conversely, any operator on $c_{00}(\Ntrl)$ which extends to a bounded
operator on $\ell^2(\Ntrl)$ is bounded on $c_{00}(\Ntrl)$ in the $\ell^2$-norm,
and the extension to $\ell^2(\Ntrl)$ is unique.

Denote the inner product on $\ell^2(\Ntrl)$ 
as $(a,b) := \sum_{n=0}^\infty \overline{a_n}b_n$, which we note
is linear in the second argument.

We shall be chiefly concerned with determining conditions on the sequence $\{a_n\}_{n=0}^\infty$
such that the associated Hankel matrix $\{a_{j+k}\}_{j,k\geq 0}$ lies in some ideal
of compact operators. According to the ``Calkin correspondence" philosophy, (explained
in detail in Appendix \ref{IdealsOfOperators}), an ideal of compact operators
can be determined by an associated rate of decay of singular values.

For a (complex separable) Hilbert space $\Hilb$, and an operator $T \in \mathcal{B}(\Hilb)$, 
we say that $T \in \mathcal{L}^{p,q}$ if $\{\mu_n\}_{n=0}^\infty \in \ell^{p,q}(\Ntrl)$.
The main goal of this chapter is to determine sufficient conditions on $\{a_n\}_{n=0}^\infty$
such that the infinite matrix $\{a_{j+k}\}_{j,k\geq 0}$ defines an operator
on $\ell^2(\Ntrl)$ that is $\mathcal{L}^{p,q}$.

The presentation here is based on the book \emph{Hankel Operators
and their Applications}, by V.V. Peller, \cite{peller}, but we will only prove the results
necessary for a basic introduction to quantised calculus.


See Appendix \ref{ClassicalHarmonicAnalysis} for the elementary properties of the Fourier transform. 

A \emph{polynomial} on $\Circ$ is a finite linear combination of the \emph{monomials}
$\{z^n\}_{n \in \Itgr}$. We call the space of polynomials $P(\Circ)$.
An \emph{analytic polynomial} is a polynomial consisting only of non-negative powers
of $z$, we denote $P_A(\Circ)$ for the space of analytic polynomials. 

It is easy to see that the Fourier transform gives a vector space isomorphism between $P(\Circ)$
and $c_{00}(\Itgr)$, and $P_A(\Circ)$ and $c_{00}(\Ntrl)$.

\section{Bounded Hankel operators}
It if of interest to determine when a Hankel operator defines
a bounded linear operator on $\ell^2(\Ntrl)$. This is answered completely by the
\emph{Nehari theorem}, which we cover now.
\begin{theorem}[Nehari]
\label{nehari}
    Let $a = \{a_j\}_{j=0}^\infty$ be a sequence. Then the 
    associated Hankel matrix $M_a$ defines a bounded linear operator on $\ell^2(\Ntrl)$
    if and only if there exists $\psi \in L^\infty(\Circ,\ha)$ such that
    \begin{equation}
        \hat{\psi}(m) = a_m
    \end{equation}
    for $m \geq 0$.
\end{theorem}
\begin{proof}
    Suppose first that there is $\psi \in L^\infty(\Circ)$
    such that $\hat{\psi}(m) = a_m$ for $m\geq 0$. 
    
    Choose $f,h \in P_A(\Circ)$, so that $\hat{f},\hat{h} \in c_{00}(\Ntrl)$.
    
    Let $g \in P_A(\Circ)$ be given by $g = \sum_{n=0}^\infty \overline{\hat{g}(n)}z^n$.
    Let $q = fg$.
    
    Then we compute,
    \begin{align}
        (\hat{h},M_a\hat{f}) &= \sum_{j,k \geq 0} \overline{\hat{h}(j)}a_{j+k}\hat{f}(k)\\
        &= \sum_{j,k\geq 0} \overline{\hat{h}(j)}\hat{\psi}(j+k)\hat{f}(k)\\
        &= \sum_{j \geq 0} \hat{\psi}(j) \sum_{k=0}^j \hat{g}(j)\hat{f}(j-k)\\
        &= \sum_{j \geq 0} \hat{\psi}(j) \hat{q}(j)\\
        &= \int_\Circ \psi(\zeta) q(\overline{\zeta}) \;d\ha(\zeta).
    \end{align}
    Hence,
    \begin{align}
        |(\hat{h},M_a\hat{f})| &\leq \|\psi\|_{\infty} \|q\|_1\\
                               &\leq \|\psi\|_\infty \|f\|_2 \|h\|_2\\
                               &= \|\psi\|_\infty \|\hat{f}\|_2\|\hat{h}\|_2.
    \end{align}
    And thus $M_a$ is bounded on $\ell^2(\Ntrl)$.
    
    Conversely, suppose that $M_a$ is bounded on $\ell^2(\Ntrl)$. 
    
    Let $\mathcal{L}$ be the linear functional on $P(\Circ)$ defined by
    \begin{equation}
        \mathcal{L}(q) := \sum_{n\geq 0} a_n \hat{q}(n).
    \end{equation}
    If $a \in \ell^1(\Ntrl)$, then $\mathcal{L}$ is bounded on $H^1(\Circ)$,
    since the inverse Fourier transform of $a$ is in $L^\infty(\Circ)$. 
    Now let us prove in this case that $\|\mathcal{L}\| \leq \|M_a\|$. 
    
    Let $q \in H^1(\Circ)$, with $\|q\|_1 \leq 1$. Then $q = fg$
    for some $f,g \in H^2(\Circ)$ with $\|f\|_2,\|g\|_2 \leq 1$. 
    
    Then we can compute,
    \begin{align} 
        |\mathcal{L}(q)| &= \left|\sum_{n=0}^\infty a_n \sum_{m=0}^n \hat{f}(m)\hat{g}(n-m)\right|\\
        &= \sum_{n,m\geq 0} a_{n+m} \hat{f}(n) \hat{g}(m)\\
        &= (M_a \hat{f},\overline{\hat{g}}). 
    \end{align}
    And hence,
    \begin{equation}
        |\mathcal{L}(q)| \leq \|M_a\|\|f\|_2\|g\|_2 \leq \|M_a\|.
    \end{equation}
    So $\mathcal{L}(q)$ is bounded on $H^1(\Circ)$ whenever $a \in \ell^1(\Ntrl)$. 
    
    Now we consider $a$ to be an arbitrary sequence such that $M_a$ is bounded. Let $r \in (0,1)$
    and
    \begin{equation}
        a^{(r)} = \{r^ja_j\}_{j\geq 0}.
    \end{equation}
    Then $a^{(r)} \in \ell^1(\Ntrl)$,
    
    Now we can see that $M_{a^{(r)}} = D_r M_a D_r$, where $D_r$
    is multiplication by the sequence $\{r^j\}_{j\geq 0}$. Since $\|D_r\| \leq 1$, 
    we must have $\|M_{a^{(r)}}\| \leq \|M_a\|$. Since $a^{(r)} \in \ell^1(\Ntrl)$, 
    we have that the linear functional
    \begin{equation}
        \mathcal{L}_r(q) := \sum_{n=0}^\infty a_nr^n \hat{q}(n)
    \end{equation}
    is bounded on $H^1(\Circ)$, and the functionals $\{\mathcal{L}_r\}_{r \in (0,1)}$
    converge strongly to $\mathcal{L}$, and are uniformly bounded. Hence $\mathcal{L}$
    is continuous on $H^1(\Circ)$. 
    
    Now by the Hahn-Banach theorem, since $\mathcal{L}$ is a linear
    functional on the subspace $H^1(\Circ)$ which has norm bounded
    by $\|M_a\|$, it is the restriction
    of a linear functional on $L^1(\Circ)$, with norm bounded by $\|M_a\|$.
    Hence $\mathcal{L}(q) = (\psi,q)$ for some $\psi \in L^\infty(\Circ)$
    with $\|\psi\|_\infty \leq \|M_a\|$. This proves the result.    
\end{proof}

The key idea of this theorem is that it relates the sequence defining
a Hankel operator with a function on $\Circ$. We can state this in a slightly more
elegant way using the following result of Fefferman; which
can be found in  the book \emph{Bounded Analytic functions} \cite[Cor 4.5, p.240]{Garnett};
\begin{proposition}
    The space $\BMO(\Circ)$ is defined as the set of measurable
    functions $f$ on $\Circ$ (modulo almost-everywhere equivalence) such that
    \begin{equation}
        \sup_I \int_I \frac{1}{\ha(I)}\left|f-\frac{1}{\ha(I)}\int_I f\;d\ha\right|\;d\ha < \infty
    \end{equation}
    where $I$ is taken over all arcs in $\Circ$.
    
    $\BMO(\Circ)$ is a Banach space when equipped with the norm,
    \begin{equation}
        \|f\|_{\BMO(\Circ)} = \sup_I \frac{1}{\ha(I)}\int_I \left|f-\frac{1}{\ha(I)}\int_I f\;d\ha\right|\;d\ha + |\hat{f}(0)|
    \end{equation}
    
    Then 
    \begin{equation}
        \BMO(\Circ) = L^\infty(\Circ)+\Proj_+L^\infty(\Circ) = \{f+\Proj_+g\;:\;f,g \in L^\infty(\Circ)\}.
    \end{equation}
\end{proposition}

Using this description of $\BMO(\Circ)$, we can prove the following,
which is an equivalent statement of the Nehari theorem, \ref{nehari}.
\begin{corollary}
    Let $a = \{a_j\}_{j=0}^\infty$ be a sequence. Then $M_a$ defines
    a bounded operator on $\ell^2(\Ntrl)$ if and only if
    \begin{equation}
        \varphi := \sum_{n=0}^\infty a_n z^n \in \BMO(\Circ)\cap H^1(\Circ).
    \end{equation}
\end{corollary}
\begin{proof}
    By theorem \ref{nehari}, $M_a$ is bounded if and only if $\varphi = \Proj_+\psi$
    for some $\psi \in L^\infty(\Circ)$. Hence if $M_a$ is bounded,
    then $\varphi \in \BMO(\Circ)\cap H^1(\Circ)$. 
    
    Conversely, if $\varphi \in \BMO(\Circ)\cap H^1(\Circ)$,
    then $\varphi = f+\Proj_+g$ for $f,g \in L^\infty$. Thus
    $\varphi = \Proj_+\varphi = \Proj_+(f+g)$, so $M_a$ is bounded.
\end{proof}

From now on, we are no longer interested in Hankel matrices $M_a$ defined by an arbitrary
sequence $a$, we are only interested in those matrices $M_a$ such that $a$
arises from the Fourier transform of a function. 
\begin{definition}
    Let $\varphi \in H^1(\Circ)$. Let $\Gamma_\varphi$
    be the Hankel matrix with $(i,j)$th entry $\hat{\varphi}(i+j)$.
\end{definition}

The properties of Hankel operators, as we shall now demonstrate in part, can be summarised
in the following table: \\
\begin{center}
\begin{tabular}{|c|c|}
\hline
$\varphi$ & $\Gamma_\varphi$\\
\hline
Rational & Finite rank\\
$\VMO$ & Compact\\
$B_{pp}^{1/p}$ & $\mathcal{L}^p$\\
$\BMO$ & Bounded\\
\hline
\end{tabular}\\
\end{center}
The left hand column of the table is a list of function spaces,
and the right hand side is a list of operator spaces. This is a table
of necessary and sufficient conditions on $\varphi$ so that $\Gamma_\varphi$
lies in some operator space.

At the moment not all of the terms in the table have been defined. The Besov
classes $B_{pp}^{1/p}$ will be introduced in Definition \ref{besovDefinition},
and the class $\VMO$ is defined in Proposition \ref{feffVMO}.

We will not prove every relation implied by the above table. In particular, we will
only prove that $\varphi \in \VMO(\Circ)$ implies that $\Gamma_\varphi$ is compact,
and that $\varphi \in B_{pp}^{1/p}$ implies that $\Gamma_\varphi \in \mathcal{L}^p$.
Using these sufficient conditions, we will be able to find sufficient conditions
on $\varphi$ so that $\Gamma_\varphi$ is in $\mathcal{L}^{p,q}$ for $p \in [1,\infty]$
and $q \in (0,\infty]$. 

More detailed results are proved in the book by V.V. Peller, \cite{Peller2003},
where both the necessity and sufficiency of all the results in the above table are proved.

\section{Finite Rank Hankel operators}
The strongest condition that we can put on a Hankel matrix $\Gamma_\varphi$
is that it is a finite rank operator on $\ell^2(\Ntrl)$. The problem
of determining $\varphi$ such that $\Gamma_\varphi$ is finite rank
was solved by Kronecker, as follows.
\begin{theorem}[Kronecker]
\label{kronecker}
    Let $\varphi \in H^1(\Circ)$, and $\Gamma_\varphi$ be the associated Hankel
    matrix. Then $\Gamma_\varphi$ defines a finite rank operator on $\ell^2(\Ntrl)$
    if and only if $\varphi$ is a rational function.
\end{theorem}
\begin{proof}
    Suppose that $\rank(\Gamma_\varphi) = n$. Then the first $n+1$
    columns of the matrix of $\Gamma_\varphi$ are linearly dependent. Let $B$
    denote the backward shift operator, $B(a_0,a_1,\ldots) := (a_1,a_2,\ldots)$
    and let $F$ be the forward shift operator, $F(a_0,a_1,\ldots) := (0,a_0,a_1,\ldots)$.
    Let $a = \hat{\varphi}$.
    
    Hence there exist complex scalars $\{c_0,c_1,\ldots,c_n\}$ not all
    equal to zero such that
    \begin{equation}
        c_0a+c_1Ba+\cdots+c_nB^na = 0.
    \end{equation}
    Now let $n,k \geq 0$. It is elementary that
    \begin{equation}
        F^n B^k a = F^{n-k}a-F^{n-k}(a_0,a_1,\ldots,a_{k-1},0,0,\ldots).
    \end{equation}
    So hence we have,
    \begin{align}
        0 &= F^n\sum_{k=0}^n c_k B^ka \\
          &= \sum_{k=0}^n c_kF^n B^ka\\
          &= \sum_{k=0}^n c_kF^{n-k}a - p
    \end{align}
    where $p$ is a finitely supported sequence. 
    
    Let $q = (c_n,c_{n-1},\ldots,c_0,0,0,\ldots)$. Then we have,
    \begin{equation}
        0 = q * a - p.
    \end{equation}
    Where the $*$ is convolution. Therefore, if we take the inverse Fourier transform,
    denotes $\check{a} = \sum_{n\geq 0} a_n z^n$ and $\check{p} = \sum_{n\geq 0} p_n z^n$,
    (the operation $s \mapsto \check{s}$ being the inverse Fourier transform), we
    get,
    \begin{equation}
        \varphi\check{a} = \check{p}.
    \end{equation}
    And hence $\varphi$ is a quotient of two polynomials.
    
    Conversely, suppose that $\varphi$ is a rational function. Suppose
    that $\varphi = p/q$, where $p,q \in P(\Circ)$. 
    Let $n = \max\{\deg p,\deg q\}$.
    If 
    \begin{equation}
        q = \sum_{k=0}^n c_{n-k}z^k
    \end{equation}
    then since $\varphi q = p$, we have
    \begin{equation}
        \sum_{k=0}^n c_k F^{n-k} a = p.
    \end{equation}
    Now multiply by $B^n$,
    \begin{align}
        B^n\sum_{k=0}^n  c_k F^{n-k} a &= \sum_{k=0}^n c_k B^k a\\
        &= 0.
    \end{align}
    
    Let $m \leq n$ be the largest number for which $c_m \neq 0$. Then $B^m a$
    is a linear combination of the $B^k a$ with $k \leq m-1$,
    \begin{equation}
        B^m a = \sum_{k=0}^{m-1} d_k B^k a
    \end{equation}
    for some coefficients $d_k$. 
    
    We now proceed by induction to show that any row is a linear combination
    of the first $n$ rows. 
    
    Let $k > m$. Then we have,
    \begin{align}
        B^k a &= B^{k-m} B^m a\\
        &= \sum_{j=0}^{m-1} d_j B^{k-m+1}a.
    \end{align}
    Since $k-m+j < k$, we have that the terms on the right hand side are
    linear combinations of the first $m$ rows by the inductive hypothesis.
    Hence $\rank(\Gamma_\varphi) \leq m$. 
\end{proof}

\section{Compactness of Hankel Operators}
If $\varphi \in L^1(\Circ)$, we are interested in conditions
on $\varphi$ such that $\Gamma_\varphi$ is compact. 

Our first result shows that Hankel matrices are continuous in their symbol.
\begin{proposition}
    Let $\varphi \in L^\infty(\Circ)$, then
    \begin{equation}
        \|\Gamma_\varphi\| \leq \|\varphi\|_\infty.
    \end{equation}
\end{proposition}
\begin{proof}
    It was shown in the proof of theorem \ref{nehari} that if $g,f$ are sequences
    of finite support, then
    \begin{equation}
        |(g,\Gamma_\varphi f)| \leq \|\varphi\|_\infty \|g\|_2\|f\|_2.
    \end{equation}
    Hence $\|\Gamma_\varphi\| \leq \|\varphi\|_\infty$.
\end{proof}

\begin{corollary}
\label{ctsCmpt}
    If $\varphi \in C(\Circ)$, then $\Gamma_\varphi$ is compact.
\end{corollary}
\begin{proof}
    Note that $\Gamma_\varphi$ is finite rank for $\varphi$ a polynomial,
    and polynomials are dense in $C(\Circ)$ with the $\|\cdot\|_\infty$
    norm. Since we have $\|\Gamma_\varphi\| \leq \|\varphi\|_\infty$,
    the map $\varphi \mapsto \Gamma_\varphi$ is continuous
    from $C(\Circ)$ to $\mathcal{B}(\ell^2(\Ntrl))$. Since
    the closure of the finite rank operators in $\mathcal{B}(\Hilb)$
    is the set of compact operators, we conclude that for
    $\varphi \in C(\Circ)$, $\Gamma_\varphi$ is compact.
\end{proof} 

To complete our characterisation of compact Hankel operators, we require
the following result of Fefferman, found in \cite{Garnett}:
\begin{proposition}
\label{feffVMO}
    The class $\VMO(\Circ)$ is the set of measurable functions $f:\Circ\rightarrow\Cplx$
    such that
    \begin{equation}
        \lim_{\ha(I)\rightarrow0} \frac{1}{\ha(I)}\int_I \left|f-\frac{1}{\ha(I)}\int_I f\;d\ha\right|\;d\ha = 0
    \end{equation}
    where the limit is over all arcs $I \subseteq \Circ$. 
    
    $\VMO(\Circ)$ is alternatively viewed as the closure of the trigonometric
    polynomials in $\BMO(\Circ)$.
    
    It is a result of Fefferman \cite{Garnett} that,
    \begin{equation}
        \VMO(\Circ) = C(\Circ)+\Proj_+C(\Circ).
    \end{equation}
\end{proposition}

So we have the following:
\begin{proposition}
    Let $\varphi \in \VMO(\Circ)$. Then $\Gamma_\varphi$ is compact.
\end{proposition}
\begin{proof}
    if $\varphi \in \VMO(\Circ)$, then by proposition \ref{feffVMO}, $\varphi = f+\Proj_+g$ 
    for $f,g \in C(\Circ)$. Hence,
    $\Proj_+\varphi = \Proj_+(f+g)$. Hence, there exists $h \in C(\Circ)$
    with $\Gamma_{\varphi} = \Gamma_h$, simply by choosing $h = f+g$. 
    This is because $\Gamma_\varphi$ depends only on the Fourier coefficients
    $\hat{\varphi}(n)$ for $n \geq 0$, so $\Gamma_{\varphi} = \Gamma_{\Proj_+\varphi}$.
    
    Hence by corollary \ref{ctsCmpt}, we see that $\Gamma_\varphi$
    is compact.
\end{proof}



\section{Hankel Operators of Trace Class}
We recall the definition of the $\mathcal{L}^1$ norm on $\mathcal{B}(\Hilb)$,
\begin{definition}
    Let $\Hilb$ be a separable Hilbert space, and let $T \in \mathcal{B}(\Hilb)$. 
    For a non-negative integer $n$, we define the $n$th singular value,
    \begin{equation}
        \mu_n(T) := \inf\{\|T-F\| \;:\;F \in \mathcal{B}(\Hilb),\rank(F) \leq n\}.
    \end{equation}
    For $p \in (0,\infty)$, we define the $\mathcal{L}^p$ norm of $T$
    as
    \begin{equation}
        \|T\|_p = \left(\sum_{n=0}^\infty |\mu_n(T)|^p\right)^{1/p}
    \end{equation}
    with the convention that $\|T\|_p = \infty$ if the sum does not
    converge. The space $\mathcal{L}^p$ is the set of $T \in \mathcal{B}(\Hilb)$
    such that $\|T\|_p < \infty$.
\end{definition}



In particular we are interested in the case $p = 1$. We are interested
in finding conditions on a function $\varphi$ holomorphic in the unit disc
such that $\Gamma_\varphi$ is in $\mathcal{L}^1$. 

\begin{lemma}
    Let $\Hilb$ be a separable Hilbert space. Suppose
    that $x,y \in \Hilb$, and let $T$ be the rank one operator
    defined by $T(\zeta) = \langle x,\zeta\rangle y$. Then $\|T\|_1 = \|x\|\|y\|$.
\end{lemma}

The answer is provided by the \emph{Besov classes}. Many different definitions
of Besov spaces can be found, but the one of most relevance to us is given below.
\begin{definition}
    \label{besovDefinition}
    We define a sequence of polynomials $\{W_n\}_{n \in \Itgr} \subset P(\Circ)$ as follows.
    First,
    \begin{equation}
        W_0 = z^{-1}+1+z.
    \end{equation}
    And now for $n > 0$, we define $W_n$ by asserting that $\widehat{W}(2^n) = 1$,
    $\widehat{W}(2^{n-1}) = 0$, $\widehat{W}(2^{n+1}) = 0$, and $\widehat{W}$
    is a linear increasing function between $2^{n-1}$ and $2^n$, and a
    linear decreasing function between $2^n$ and $2^{n+1}$. We
    assert that $\widehat{W}(n)$ is symmetric in $n$, and is zero for all
    values not already defined.
    
    Now, for $p,q > 0$, and $s \geq 0$, we define the \emph{Besov class}
    $B_{pq}^s(\Circ)$ to be the space of distributions $f$ on $\Circ$ such that
    \begin{equation}
        \sum_{n\geq 0} 2^{nsq} \|W_n*f\|_{p}^q < \infty.
    \end{equation}  
    We shall denote $B_{pp}^s$ as $B_p^s$.
\end{definition}

In particular, we are going to prove that if $\varphi \in B_1^1(\Circ)$, then
$\Gamma_\varphi \in \mathcal{L}^1$. First, we need a lemma.
\begin{lemma}
    Let $f \in P_A(\Circ)$ be an analytic polynomial of degree at most $m$. Then,
    \begin{equation}
        \|\Gamma_f\|_1 \leq (m+1)\|f\|_1.
    \end{equation}
\end{lemma}
\begin{proof}
    Let $\zeta \in \Circ$, now define the following elements
    of $\ell^2(\Ntrl)$, 
    \begin{align}
        x_\zeta(j) &= \begin{cases}
            \zeta^j,\;0 \leq j \leq m,\\
            0,\;j > m
        \end{cases}\\
        y_\zeta(j) &= \begin{cases}
            f(\zeta)\zeta^{-k},\;0\leq k \leq m,\\
            0,\;k > m.
        \end{cases}
    \end{align}
    That is, $x_\zeta = (1,\zeta,\zeta^2,\ldots,\zeta^m,0,0,\ldots)$
    and $y_\zeta = f(\zeta)\overline{x_\zeta}$.
    
    Let $A_\zeta$ be the rank one operator, $A_\zeta(x) = (x_\zeta,x)y_\zeta$,
    so that $\|A_\zeta\|_1 = \|x_\zeta\|_2\|y_\zeta\|2 = (m+1)|f(\zeta)|$
    
    Then we have a componentwise equality of infinite matrices,
    \begin{equation}
        \Gamma_f = \int_\Circ A_\zeta\;d\ha(\zeta).
    \end{equation}
    Hence, $\|\Gamma_f\|_1 \leq (m+1)\|f\|_1$ by the triangle inequality.
\end{proof}
\begin{theorem}
    Let $\varphi \in B_1^1$. Then $\Gamma_\varphi \in \mathcal{L}^1$. 
\end{theorem}
\begin{proof}
    We have the following $L^\infty$-convergent sequence,
    \begin{equation}
        \varphi = \sum_{n\geq 0} W_n*\varphi.
    \end{equation}
    Hence,
    \begin{equation}
        \Gamma_\varphi = \sum_{n\geq 0} \Gamma_{W_n*\varphi}.
    \end{equation}
    So since the degree of $W_n$ is $2^{n+1}$, we have
    \begin{equation}
        \|\Gamma_\varphi\|_1 \leq \sum_{n\geq 0} 2^{n+1}\|W_n*\varphi\|_1.
    \end{equation}
\end{proof}

This proves the sufficiency of the condition $\varphi \in B_1^1$ so that $\Gamma_\varphi$
is trace class. The proof of the necessity of this condition is more difficult,
\begin{theorem}
    Let $\varphi$ be a function holomorphic in the unit disc. Then
    if $\Gamma_\varphi \in \mathcal{L}^1$, then $\varphi \in B_1^1$. 
\end{theorem}
\begin{proof}
    Define a pair of sequences of polynomials $\{Q_n\}_{n=0}^\infty$ as follows,
    \begin{equation}
        \widehat{Q}_n(k) = \begin{cases}
            0, \;k \leq 2^{n-1}\\
            1-\frac{|k-2^n|}{2^{n-1}},\;2^{n-1}\leq k \leq 2^n+2^{n-1},\\
            0\;k \geq 2^n+2^{n-1}.
        \end{cases}
    \end{equation}
    and a sequence $\{R_n\}_{n=0}^\infty$,
    \begin{equation}
        \widehat{R}_n(k) = \begin{cases}
                0,\;k \leq 2^n\\
                1-\frac{|k-2^n-2^{n-1}|}{2^{n-1}},\;2^{n}\leq 2^{n+1}\\
                0,\;k \geq 2^{n+1}.
        \end{cases}
    \end{equation}
    This is a decomposition of the sequence $\{W_n\}_{n=0}^\infty$, 
    given by $W_n = Q_n+\frac{1}{2}R_n$. 
    
    First we prove that
    \begin{equation}
        \sum_{n\geq 0} 2^{2n+1}\|Q_{2n+1}*\varphi\|_1 < \infty.
    \end{equation}
    
    To this end, we wish to construct an operator $B$
    such that
    \begin{equation}
        \langle \Gamma_\varphi,B\rangle = \sum_{n\geq 0} 2^{2n} \|Q_{2n+1}*\varphi\|_1.
    \end{equation}
    
    Now define the sequence of squares,
    for $n\geq 1$,
    \begin{equation}
        S_n = [2^{2n-1},2^{2n-1}+2^{2n}-1]\times [2^{2n-1}+1,2^{2n-1}+2^{2n}].
    \end{equation}
    Note that this sequence is pairwise disjoint.
    
    Let $\{\psi_n\}_{n=0}^\infty$ be a sequence in $L^\infty(\Circ)$, yet to be
    defined with $\|\psi_n\|_{\infty} \leq 1$. Now we
    define the matrix $B = \{B_{j,k}\}_{j,k\geq 0}$ by
    \begin{equation}
        B_{j,k} = \begin{cases}
            \widehat{\psi}_n(j+k),(j,k) \in S_n,n\geq 1,\\
            0,(j,k) \notin \bigcup_{n\geq 1} S_n.
        \end{cases}
    \end{equation}
    We wish to prove that $B$ is bounded, and in fact $\|B\|\leq 1$. 
    Let $\{e_n\}_{n\geq 0}$ be the standard basis for $\ell^2(\Ntrl)$,
    with $e_n(m) = \delta_{n,m}$. Define the subspaces
    \begin{align}
        \Hilb_n &= \span\{e_j\;:\;2^{2n-1}\leq j \leq 2^{2n-1}+2^{2n}-1\},\\
        \Hilb_n' &= \span\{e_j\;:\;2^{2n-1}+1\leq j\leq 2^{2n-1}+2^{2n}\}.
    \end{align}
    Let $P_n$ and $P_n'$ be the orthogonal projection onto $\Hilb_n$ and $\Hilb_n'$
    respectively.
    So that
    \begin{equation}
        B = \sum_{n\geq 1} P_n'\Gamma_{\psi_n}P_n,
    \end{equation}
    where $P_n$ and $P_n'$ are the orthogonal projections onto $\Hilb_n$
    and $\Hilb_n'$ respectively.
    
    Now since the spaces $\{\Hilb_n\}_{n\geq 1}$ are pairwise orthogonal,
    as are the spaces $\{\Hilb_n'\}_{n\geq 1}$, we have
    \begin{align}
        \|B\| &\leq \sup_{n\geq 1} \|P_n'\Gamma_{\psi_n}P_n\|\\
         &\leq \sup_{n} \|\Gamma_{\psi_n}\|\\
         &\leq \sup_{n} \|\psi_n\|_\infty \\
         &\leq 1.
    \end{align}
    
    Now, we compute
    \begin{align}
        \langle \Gamma_\varphi,B \rangle &= \sum_{n\geq 1} \langle \Gamma_\varphi,P_n'\Gamma_{\psi_n}P_n\rangle\\
        &= \sum_{n\geq 1} \sum_{j=2^{2n}}^{2^{2n}+2^{2n+1}}(2^{2n}-|j-2^{2n+1}|\overline{\widehat{\varphi}}(j)\widehat{\psi_n}(j)\\
        &= \sum_{n\geq 1} 2^{2n} (Q_{2n+1}*\varphi,\psi_n).
    \end{align}
    Now, using the sharpness of H\"older's inequality, we can choose
    a sequence $\{\psi_n\}_{n=0}^\infty$ so that $\langle Q_{2n+1}*\varphi,\psi_n\rangle$
    is arbitrarily close to $\|Q_{2n+1}*\varphi\|_1$. Hence,
    \begin{equation}
        \sum_{n\geq 1}2^{2n+1}\|Q_{2n+1}*\varphi\|_1 = 2\langle \Gamma_\varphi,B\rangle \leq 2\|\Gamma_\varphi\|_1.
    \end{equation}
    In exactly the same way, we may prove that
    \begin{equation}
        \sum_{n\geq 1}2^{2n}\|Q_{2n}*\varphi\|_1 < \infty
    \end{equation} 
    that
    \begin{equation}
        \sum_{n\geq 0} 2^{2n+1} \|R_{2n+1}*\varphi\|_1 < \infty
    \end{equation}
    and
    \begin{equation}
        \sum_{n\geq 1} 2^{2n}\|R_{2n}*\varphi\|_1 < \infty
    \end{equation}
    and therefore that $\varphi \in B_1^1$.
\end{proof} 

\begin{remark}
    We thus conclude that
    \begin{equation}
        \frac{1}{6}\sum_{n\geq 1}2^n \|W_n*\varphi\|_1 \leq \|\Gamma_\varphi\|_1 \leq 2\sum_{n\geq 0} 2^n\|W_n*\varphi\|_1.
    \end{equation}
\end{remark}

\section{Interpolation}
For this section, $\mathcal{L}^\infty$ denotes the space of compact operators.

Up to now we have proved necessary and sufficient conditions
on $\varphi$ so that $\Gamma_\varphi$ lies in a certain ideal one at a time.
In particular, we have with great effort proved that $\Gamma_\varphi \in \mathcal{L}^1$
if and only if $\varphi \in B_{11}^1(\Circ)$.
This amounts to a continuous
injection:
\begin{equation}
\label{emb1}
    B_{11}^1(\Circ) \to \mathcal{L}^1
\end{equation}
with equivalence of norms.
We denote $\Gamma\mathcal{L}^\infty$
as the class of compact Hankel operators.

We also know that we have an injection
\begin{equation}
\label{emb2}
    \VMO(\Circ) \to \mathcal{L}^\infty.
\end{equation}


It is a remarkable fact that using the embeddings \ref{emb1}
and \ref{emb2} alone we can find sufficient conditions on $\varphi$
so that $\Gamma_\varphi \in \mathcal{L}^{p,q}$ for $p\in [1,\infty]$,$q \in (0,\infty]$.

We accomplish this via interpolation theory.
The basic material is covered in Appendix \ref{Interpolation}. The pair $(B_{11}^1(\Circ),\VMO(\Circ))$.
The map $\varphi \mapsto \Gamma_\varphi$ takes the pair
$(B_{11}^1(\Circ),\VMO(\Circ))$ to $(\mathcal{L}^1,\mathcal{L}^\infty)$.
Hence for any interpolation functor $F:\NLS_1\to\NLS$ (using the notation
of Appendix \ref{Interpolation}, we have that if $\varphi \in F(B_{11}^1(\Circ),\VMO(\Circ))$,
then $\Gamma_{\varphi} \in F(\mathcal{L}^1,\mathcal{L}^\infty)$.

In order to therefore find sufficient conditions on $\varphi$ so that $\Gamma_\varphi \in \mathcal{L}^{p,q}$,
we simply need to find an interpolation functor $F_{p,q}$ such that $F_{p,q}(\mathcal{L}^1,\mathcal{L}^\infty) = \mathcal{L}^{p,q}$.

It turns out that there is indeed such a functor, the $K$ functor from real interpolation theory.
For a definition see Appendix \ref{Interpolation}. We can choose $F_{p,q} = K(\cdot,\cdot)_{\theta,q}$
where $\theta = 1-p^{-1}$. This is due to the following result:
\begin{proposition}
\label{LpqInterp}
    Let $p \in (0,\infty)$ and $q \in (0,\infty]$. If $\theta = 1-p^{-1}$, then $K(\mathcal{L}^1,\mathcal{L}^\infty)_{\theta,q} = \mathcal{L}^{p,q}$.
\end{proposition}
\begin{proof}
    The details of this interpolation result are included in \cite{DDP92}.
    
    The key estimate is as follows.
    Let $T \in \mathcal{L}^1+\mathcal{L}^\infty = \mathcal{L}^\infty$.
    Using a result from G.E. Karadzhov \cite{Karadzhov},
    the $K$ functional, $K(t,T,\mathcal{L}^1,\mathcal{L}^\infty)$, given in
    definition \ref{Kdefinition}, can be estimated by
    \begin{equation}
        c_1\left(\sum_{j=0}^n \mu_j(T)^p\right)^{1/p} \leq K(t,T,\mathcal{L}^1,\mathcal{L}^\infty) \leq c_2\left(\sum_{j=0}^n \mu_j(T)^p\right)^{1/p},
    \end{equation}
    for $n^{1/p} \leq t \leq (n+1)^{1/p}$, for some positive constants $c_1,c_2$. This
    estimate can be found in \cite{Karadzhov}.
\end{proof}


%The following is proved in \cite{DDP92}:
%\begin{lemma}
%    Let $K$ be the real interpolation functor, described in \cite{interp}. 
%    Let $p,q \in (0,\infty]$
%    Then
%    \begin{equation}
%        K(\mathcal{L}^1,\mathcal{K})_{\theta,q} = \mathcal{L}_{p,q}.
%    \end{equation} 
%    for $p = (1-\theta)^{-1}$.
%\end{lemma}


%\begin{corollary}
%    Hence, we have that $\Gamma_\varphi \in \mathcal{L}_{p,q}$
%    if $\varphi \in K(B_1^1,\VMO)_{\theta,q}$, where $p = (1-\theta)^{-1}$.
%\end{corollary}

So we have shown that if $\varphi \in K(B_{11}^1(\Circ),\VMO(\Circ))_{1-1/p,q}$,
then $\Gamma_\varphi \in \mathcal{L}^{p,q}$. Peller \cite[Theorem 4.4, p. 256]{Peller2003} shows
that this condition is not just sufficient but also necessary. Of particular interest
is the case $p = q$. This is solved by the following result, which is \cite[Theorem 4.3, p.255]{Peller2003}:
\begin{proposition}
    Let $p \in (1,\infty)$. Then $K(B_{11}^1(\Circ),\VMO(\Circ)) = B_{pp}^{1/p}(\Circ)$. 
\end{proposition}

\section{Extrapolation}
We have determined sufficient conditions for $\Gamma_\varphi \in \mathcal{L}^{p,q}$,
for $p \in [1,\infty]$ and $q \in (0,\infty]$.
We now turn our attention to more exotic ideals of $\mathcal{B}(\ell^2(\Ntrl))$. The
Macaev-Dixmier ideal $\M_{1,\infty}$ is described in detail Appendix \ref{IdealsOfOperators}.

Most important for our purposes is the equivalence of norms, proved in Theorem 4.5 of \cite{CRSS},
\begin{equation}
    \|x\|_{\M_{1,\infty}} = \limsup_{s \downarrow 0} s\|x\|_{\mathcal{L}_{s+1}}.
\end{equation}

First we need the following result, proved in the proof of \cite[Theorem 3.1,p.250]{Peller2003}.
\begin{proposition}
    Let $\varphi \in H^1(\Circ)$, and let $p \in (1,2)$. Then there is a constant $C$
    not depending on $p$ such that
    \begin{equation}
        \|\Gamma_{\varphi}\|_{\mathcal{L}^p}^p \leq 2^{1-p} \sum_{n\geq 0} 2^n\|W_n*\varphi\|_p^p
    \end{equation}
    Where the right hand side is defined to be $\|\varphi\|_{B_{pp}^{1/p}}$.
\end{proposition}

Hence, we have
\begin{proposition}
    Let $\varphi$ be a function on $\Circ$ such that $\limsup_{s \downarrow 0} s\|\varphi\|_{B_{s+1,s+1}^{1/(s+1)}} < \infty$.
    Then $\qd \varphi \in \M_{1,\infty}$.
\end{proposition}


There is an alternative characterisation of Besov
classes on the circle, which we refer to here,
\begin{proposition}
\label{altBesov}
    Let $\zeta,\tau \in \Circ$. For a function
    $f:\Circ\to\Cplx$, define
    \begin{equation}
        \Delta_\tau f(\zeta) = f(\tau\zeta)-f(\zeta).
    \end{equation}
    Then, let $s > 0$, $p,q \in [1,\infty]$ and $n$ be an integer $n > s$,
    \begin{equation}
        B_{pq}^s(\Circ) = \left\{f \in L^p\;:\;\int_\Circ \frac{\|\Delta^n_\tau f\|_p^q}{|1-\tau|^{1+sq}}\;d\ha(\tau) < \infty\right\}
    \end{equation}
    and the choice of $n$ is irrelevant.
\end{proposition}
A proof of this proposition can be found in [cite].

This implies the following,
\begin{proposition}
    Let $\varphi \in H^1(\Circ)$ satisfy,
    \begin{equation}
        \limsup_{s\downarrow 0} s\int_{\Circ}\frac{\|\Delta^2_\tau \varphi\|_{s+1}^{s+1}}{|1-\tau|^2}\;d\ha(\tau) < \infty.
    \end{equation}
    Then $\Gamma_\varphi \in \M_{1,\infty}$.
\end{proposition}



